Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Structure

### 2017-03-08 documents/TriangleScenarioArXiv/ts.tex
changed inequalities in the appendixes to reflect their true form
fixed whitespace around a particular figure

    \begin{center}
    \begin{figure}
    \begin{subfigure}[b]{.48\linewidth}
    \includegraphics[width=\linewidth]{../../figures/noise/noise_2017.pdf}
    \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
    \end{subfigure}
    \begin{subfigure}[b]{.48\linewidth}
    \includegraphics[width=\linewidth]{../../figures/noise/noise_2017_lims.pdf}
    \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
    \end{subfigure}
    \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
    \end{figure}
    \end{center}

@@

    Finding larger violations to compatibility inequalities is nothing more that a numerical optimization (specifically minimization) of $f\br{\la}$. Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence. Specifically, the BFGS method~\cite[p. 142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p. 238]{Nocedal_2000} were used along with a hybrid method called Basin Hopping~\cite{Wales_1997}.

@@

    \clearpage
    \section{Large Triangle Structure Inequalities}
    \subsection{Web Inflation Inequality}
    \label{sec:web_inequality}
    The following is a causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
    \begin{center}
        % TODO [TC] replace this inequality with correct one
        \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
    \end{center}
    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
    \clearpage
    \subsection{Symmetric Web Inflation Inequality}
    \label{sec:symmetic_web_inequality}
    The following is a symmetric causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
    \begin{center}
        % TODO [TC] replace this inequality with correct one
        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
    \end{center}
    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for the sum over permutations:
    \[ \bs{P(113)P(330)}_3 = P(113)P(330) + P(131)P(303) + P(311)P(033) \]

>>>>

    \begin{figure}
    \begin{subfigure}[b]{.48\linewidth}
    {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017.pdf}}
    \caption{Complete range of noise parameters $\vep$.}\label{fig:noise}
    \end{subfigure}
    \begin{subfigure}[b]{.48\linewidth}
    {\centering\includegraphics[width=\linewidth]{../../figures/noise/noise_2017_lims.pdf}}
    \caption{\Cref{fig:noise} zoomed onto relevant region.}\label{fig:noise_zoomed}
    \end{subfigure}
    \caption{Inequality violations when subjected to uniform noise. Each inequality is normalized so that maximum violation is $-1$.}\label{fig:master_noise}
    \end{figure}

@@

    Finding larger violations to compatibility inequalities is nothing more that a numerical optimization (specifically minimization) of $f\br{\la}$. Since the inequalities themselves are polynomial and the space of quantum-accessible distributions is non-convex, a number of optimization methods were used in an attempt to eliminate any issues associated with local minima or ill-conditioned convergence. Specifically, the BFGS method~\cite[p. 142]{Nocedal_2000} and the Nelder-Mead simplex method~\cite[p. 238]{Nocedal_2000} were used along with a method called Basin Hopping~\cite{Wales_1997}, which is a hybrid between simulated annealing and gradient descent-based methods.

@@

    \clearpage
    \section{Large Triangle Structure Inequalities}
    \subsection{Web Inflation Inequality}
    \label{sec:web_inequality}
    The following is a causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
    \begin{center}
        \vspace{-0.2in}
        \includegraphics[width=\linewidth]{../../figures/inequalities/no_symwitness_ineq_print_standalone}
    \end{center}
    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$.
    \clearpage
    \subsection{Symmetric Web Inflation Inequality}
    \label{sec:symmetic_web_inequality}
    The following is a symmetric causal compatibility inequality for the Triangle structure that is violated by the Fritz distribution outlined in \cref{sec:fritz_distribution} and was derived using the Web inflation of \cref{fig:the_web_inflation}.
    \begin{center}
        \vspace{-0.2in}
        \includegraphics[width=\linewidth]{../../figures/inequalities/MosekCertFritzSym_ineq_standalone}
    \end{center}
    Note: $\prob\br{abc}$ is shorthand for $\prob[ABC]\br{abc}$ and $\bs{P(113)P(330)}_3$ is shorthand for the sum over permutations:
    \[ \bs{P(113)P(330)}_3 = P(113)P(330) + P(131)P(303) + P(311)P(033) \]
